---
title: "Exercise 1"
output: html_notebook
---
Loading packages is a must
```{r}
library(tidyverse)
library(dplyr)
library(tsibble)
library(feasts)
library(stringr)
library(lubridate)
library(anytime)
library(ggplot2)
library(ggthemes)
library(knitr)
library(kableExtra)
library(DT)
library(htmltools)
library(reshape2) #to be used with tidyverse and gglopt2
```


First of all, we need to read all the files. This is my very lousy version.

```{r}
library(readr)
library(dplyr)
AXP <- data.frame(read_csv('Data/AXP.txt', col_types = cols()))
BA <- data.frame(read_csv('Data/BA.txt', col_types = cols()))
CAT <- data.frame(read_csv('Data/CAT.txt', col_types = cols()))
CSCO <- data.frame(read_csv('Data/CSCO.txt', col_types = cols()))
CVX <- data.frame(read_csv('Data/CVX.txt', col_types = cols()))
DD <- data.frame(read_csv('Data/DD.txt', col_types = cols()))
DIS <- data.frame(read_csv('Data/DIS.txt', col_types = cols()))
GE <- data.frame(read_csv('Data/GE.txt', col_types = cols()))
GS <- data.frame(read_csv('Data/GS.txt', col_types = cols()))
HD <- data.frame(read_csv('Data/HD.txt', col_types = cols()))
IBM <- data.frame(read_csv('Data/IBM.txt', col_types = cols()))
INTC <- data.frame(read_csv('Data/INTC.txt', col_types = cols()))
JNJ <- data.frame(read_csv('Data/JNJ.txt', col_types = cols()))
JPM <- data.frame(read_csv('Data/JPM.txt', col_types = cols()))
KO <- data.frame(read_csv('Data/KO.txt', col_types = cols()))
MCD <- data.frame(read_csv('Data/MCD.txt', col_types = cols()))
MMM <- data.frame(read_csv('Data/MMM.txt', col_types = cols()))
MRK <- data.frame(read_csv('Data/MRK.txt', col_types =  cols()))
MSFT <- data.frame(read_csv('Data/MSFT.txt', col_types = cols()))
NKE <- data.frame(read_csv('Data/NKE.txt', col_types =  cols()))
PFE <- data.frame(read_csv('Data/PFE.txt', col_types = cols()))
PG <- data.frame(read_csv('Data/PG.txt', col_types = cols()))
SPY <- data.frame(read_csv('Data/SPY.txt', col_types = cols()))
TRV <- data.frame(read_csv('Data/TRV.txt', col_types = cols()))
UNH <- data.frame(read_csv('Data/UNH.txt', col_types =  cols()))
UTX <- data.frame(read_csv('Data/UTX.txt', col_types = cols()))
V <- data.frame(read_csv('Data/V.txt', col_types = cols()))
VZ <- data.frame(read_csv('Data/VZ.txt', col_types = cols()))
WMT <- data.frame(read_csv('Data/WMT.txt', col_types = cols()))
XOM <- data.frame(read_csv('Data/XOM.txt', col_types = cols()))
```

OK, so now we have these files, which are TOO BIG. Let's first clean the data to get it from 2000 onwards.
```{r}
clean_data <- function(ticker) {
  ##In this function, we're going to first convert the Date column to date:
 
     ticker$Date <- as.Date(ticker$Date, '%m/%d/%Y')

  
  ## Then, we want to restrict it from 2000 onwards
     new_ticker <- filter(ticker, format(ticker$Date, '%Y') >= 2000)
     ##We need to make the left join first to create NA for all MINUTES
     minute_list <- sort(unique(new_ticker$Time)) 
     day_list <- sort(unique(new_ticker$Date))
     minute_df <- data.frame('Time' = minute_list) ##I need a minute df
     day_df <- data.frame('Date' = day_list) ##I need a day df
     day_minute_df <- left_join(day_df, minute_df, character()) ##I create a df with all dates and all possible minutes
     new_ticker <- left_join(day_minute_df, new_ticker, by = c('Time', 'Date')) ##Then we left join this bad boy and we're DONE
     new_ticker$minute_return <- (new_ticker$Close - lag(new_ticker$Close))/ new_ticker$Close ##Return of level is p_t - p_{t-1} / p_{t-1}
     new_ticker$minute_log_return <- log(new_ticker$Close) - log(lag(new_ticker$Close)) ##Log return: log(p_t) - log(p_{t-1})
     
  return(new_ticker)
}
```


Now, let's clean ALL the data.
```{r}
AXP <- clean_data(AXP)
BA <-clean_data(BA)
CAT <- clean_data(CAT)
CSCO <- clean_data(CSCO)
CVX <- clean_data(CVX)
DD <-clean_data(DD)
DIS <- clean_data(DIS)
GE <-clean_data(GE)
GS <-clean_data(GS)
HD <-clean_data(HD)
IBM <- clean_data(IBM)
INTC <- clean_data(INTC)
JNJ <- clean_data(JNJ)
JPM <- clean_data(JPM)
KO <-clean_data(KO)
MCD <- clean_data(MCD)
MMM <- clean_data(MMM)
MRK <-clean_data(MRK)
MSFT <- clean_data(MSFT)
NKE <-clean_data(NKE)
PFE <- clean_data(PFE)
PG <-clean_data(PG)
SPY <- clean_data(SPY)
TRV <- clean_data(TRV)
UNH <-clean_data(UNH)
UTX <- clean_data(UTX)
V <- clean_data(V)
VZ <-clean_data(VZ)
WMT <- clean_data(WMT)
XOM <- clean_data(XOM)
```
OK, now let's create our daily variables.

```{r}
AXP %>% group_by(Date) %>% summarise(daily=sum(minute_log_return,na.rm=T), RV = sum(minute_log_return^2, na.rm = T), VOL = sum(Volume, na.rm = T), log_RV = log(sum(minute_log_return^2, na.rm = T)) ) ##This works as intended, just creates our daily dataframe. Therefore
##I'll turn this logic into a function and create daily dataframes for all of these tickers. 
```
Seeing that my handcrafted example works, it's time to make it into a proper function to create our daily dataframes
```{r}
make_daily_data <- function(clean_ticker){
  daily_ticker <- clean_ticker %>% group_by(Date) %>% summarise(daily=sum(minute_log_return,na.rm=T), RV = sum(minute_log_return^2, na.rm = T), VOL = sum(Volume, na.rm = T), log_RV = log(sum(minute_log_return^2, na.rm = T)) )
  
  
}
```
Now, we apply this function for all tickers, just like before.
```{r}
daily_AXP <- make_daily_data(AXP)
daily_BA <-make_daily_data(BA)
daily_CAT <- make_daily_data(CAT)
daily_CSCO <- make_daily_data(CSCO)
daily_CVX <- make_daily_data(CVX)
daily_DD <-make_daily_data(DD)
daily_DIS <- make_daily_data(DIS)
daily_GE <-make_daily_data(GE)
daily_GS <-make_daily_data(GS)
daily_HD <-make_daily_data(HD)
daily_IBM <- make_daily_data(IBM)
daily_INTC <- make_daily_data(INTC)
daily_JNJ <- make_daily_data(JNJ)
daily_JPM <- make_daily_data(JPM)
daily_KO <-make_daily_data(KO)
daily_MCD <- make_daily_data(MCD)
daily_MMM <- make_daily_data(MMM)
daily_MRK <-make_daily_data(MRK)
daily_MSFT <- make_daily_data(MSFT)
daily_NKE <-make_daily_data(NKE)
daily_PFE <- make_daily_data(PFE)
daily_PG <-make_daily_data(PG)
daily_SPY <- make_daily_data(SPY)
daily_TRV <- make_daily_data(TRV)
daily_UNH <-make_daily_data(UNH)
daily_UTX <- make_daily_data(UTX)
daily_V <- make_daily_data(V)
daily_VZ <-make_daily_data(VZ)
daily_WMT <- make_daily_data(WMT)
daily_XOM <- make_daily_data(XOM)
```

Now, for a simple plot:

```{r}
ggplot(daily_AXP, aes(x= 100* min(0.0001,RV))) + geom_histogram(bins = 1000) 
```



This was the very stupid function we tried to make work, but honestly, this is useless.
```{r}
library(dplyr)

make_data <- function(ticker, flag = 0){
  ##So here's the deal: I want a list of dataframes, all with the same length of minutes.
  ##But i want every element of this list to be a list in itself: the first element is the DATE of the dataframe, the second is the dataframe itself. 
  clean_ticker <- clean_data(ticker, flag)
  ##Create a list of ALL existing minutes
  minute_list <- sort(unique(clean_ticker$Time))
  minute_df <- data.frame('Time' = minute_list) ##This df is      used only for the left join 
  dias <- unique(clean_ticker$Date)
  n <- length(dias)
 ## arr <- array(NA, dim = c(390, dim(clean_ticker)[2], n)) deprecated
  list <- vector(mode = "list", length =  n)
  names(list) <- dias ##I also want to NAME the elements of the list to know which date it is.
  for(j in 1:n){
    day_df <- clean_ticker[clean_ticker$Date == dias[j],]
    adj_day_df <- left_join(minute_df, day_df, by = 'Time') ##This is the dataframe with all data for all possible minutes, whether they have observations that day or not
    inner_list <-  vector(mode = 'list', length = 390)  ##Creates the inner list
    names(inner_list) <- minute_list ##I want to know WHICH MINUTE i'm referencing. 
    list[[j]] <- inner_list ##Assign this inner list as the j-th element of our day list!
    for (minute in 1:390){ #Now we loop over all possible minutes
            inner_variable_list <- vector(mode = 'list', length = 9) #This will have the length equal to number of variables of interest
            names(inner_variable_list) <- c("Day", "Month", "Year", "Open", "Close", "Low", "High", "Volume","r_cc")
      
            list[[j]][[minute]] <- inner_variable_list #each minute of the day is effectively receiving the vector of variables, and we`ll fill this vector next. Here, we explicit that list[[j]][[min]] is a list on its own, by associating it with inner_variable_list, which is a list
      
            df_minute <- adj_day_df[adj_day_df$Time == minute_list[minute],] ##We open the dataframe minute by minute

        
            df_minute_minus <- adj_day_df[adj_day_df$Time == minute_list[minute-1],]
      
      #finally, a minute of day j is receiving relevant economic variables	      

            list[[j]][[minute]][[1]] <- format(df_minute$Date,'%d')
            list[[j]][[minute]][[2]] <- format(df_minute$Date,'%m')
            list[[j]][[minute]][[3]] <- format(df_minute$Date,'%Y')
            list[[j]][[minute]][[4]] <- df_minute$Open
            list[[j]][[minute]][[5]] <- df_minute$Close
            list[[j]][[minute]][[6]] <- df_minute$Low
            list[[j]][[minute]][[7]] <- df_minute$High
            list[[j]][[minute]][[8]] <- df_minute$Volume
            list[[j]][[minute]][[9]] <- log((df_minute$Close)/(df_minute_minus$Close)) ##Changed to be the log return.
                        }
      
                }
    
  
  return(list)
}

```
Now, we want to apply the function to all of our dataframes, finally creating the tensors we needed
```{r}
AXP_t <-  make_data(AXP)
BA_t <- make_data(AXP)
CAT_t <-  make_data(AXP)
CSCO_t <-  make_data(AXP)
CVX_t <-  make_data(AXP)
DD_t <- make_data(AXP)
DIS_t <-  make_data(AXP)
GE_t <- make_data(AXP)
GS_t <- make_data(AXP)
HD_t <- make_data(AXP)
IBM_t <-  make_data(AXP)
INTC_t <-  make_data(AXP)
JNJ_t <-  make_data(AXP)
JPM_t <-  make_data(AXP)
KO_t <- make_data(AXP)
MCD_t <-  make_data(AXP)
MMM_t <-  make_data(AXP)
MRK_t <-  make_data(AXP)
MSFT_t <-  make_data(AXP)
NKE_t <-  make_data(AXP)
PFE_t <-  make_data(AXP)
PG_t <- make_data(AXP)
SPY_t <-  make_data(AXP)
TRV_t <-  make_data(AXP)
UNH_t <-  make_data(AXP)
UTX_t <-  make_data(AXP)
V_t < make_data(AXP, flag = 1)
VZ_t <- make_data(AXP)
WMT_t <-  make_data(AXP)
XOM_t <-  make_data(AXP)
```
```{r}
clean_ticker <- clean_data(AXP)
minute_list <- sort(unique(clean_ticker$Time))
minute_df <- data.frame('Time' = minute_list) ##T
dias <- unique(clean_ticker$Date)

n <- length(dias)
j = 1 

list <- vector(mode = "list", length =  n)

df1 <- clean_ticker[clean_ticker$Date == dias[j],]

df2 <- left_join(minute_df, df1, by = 'Time') ##This is the dataframe with all data for all possible minutes, whether they have observations that day or not
list[[j]] <- vector(mode = 'list', length = 390) ##Creates the inner list
minute = 1
list[[j]][[minute]] <- vector(mode = 'list', length = 2)
df_minute <- df2[df2$Time == minute_list[minute],]
df_minute_minus <- df2[df2$Time == minute_list[minute-1],]##We open the dataframe minute by minute
list[[j]][[minute]][[1]] <- df_minute$Open
list[[j]][[minute]][[2]] <- (df_minute$Close - df_minute_minus$Close)/(df_minute_minus$Close)
      
minute_df[1:1,]
x <- sort(unique(clean_ticker$Time))
x_df <- data.frame("Time" = x)
```
